IPv6 over Low-Power Wireless Personal Area Networks\\ MSc. Thesis Proposal

### 2009-12-16 trunk/doc/msc-proposal/msc-routing.tex
proposal: ND

\chapter{6LoWPAN Routing}\label{ch:routing}
Neither the IEEE 802.15.4 \cite{ieee802.15.4} standard nor the 6LoWPAN format specification \cite{rfc4944} define how mesh topologies could be obtained and maintained. In 6LoWPAN routing can be perforem either in the IP-layer, using a Route Over approach, or in the adaptation layer described in Section \ref{subsec:mesh.header}, using the Mesh Under approach.

>>>>

\chapter{6LoWPAN Routing}\label{ch:routing}
Neither the IEEE 802.15.4 \cite{ieee802.15.4} standard nor the 6LoWPAN format specification \cite{rfc4944} define how mesh topologies could be obtained and maintained. In 6LoWPAN routing can be performed either in the IP-layer, using a Route Over approach, or in the adaptation layer described in Section \ref{subsec:mesh.header}, using the Mesh Under approach. The Mesh Under approach performs the multi-hop communication below the IP link and therefore a 6LoWPAN is seen as a single IP link.
